Automatic Code Optimizations on GPU Architectures

### 2018-01-11 Paper.tex
Finale2

		Data prefetching is relatively simple to use in the application and performs only one additional load operation, which copies memory from the global memory to the local memory. If data is loaded at this point that is no longer needed, the access times to the global memory for other threads increase unnecessarily, but the execution of the current thread is slowed down only marginally, since the load operation is executed in parallel and does not block the process flow of the thread as long as the data is not required.

		The redistribution of data during the elimination of partition camping has more problems if used incorrectly. Two variants must be considered.
		In extreme cases, where all data is correct, the performance gain can be reversed if the data is redistributed. 
		In a mixed case, where some data is stored unfavourably, it can lead to slight performance changes due to incorrect redistribution, but in both directions.

		Contrary to all other categories, thread block merging and thread merging have to be considered separately, since thread block merging does not normally change the number of threads, while thread merging is halved.

@@

		If thread merging is incorrectly applied, the number of threads will be halved. This doubles the computing time \cite{torres2011understanding}.

@@

	Yi Yang et. al. wrote a paper on "A GPGPU Compiler for Memory Optimization Parallelism Management" which explains how to implement the optimizations presented in this paper. Further optimizations are also presented and these optimizations are tested using examples such as matrix multiplication with large matrices \cite{yang2010gpgpu}.

	Ashwin M. Aji et al. wrote an article on "Bounding the Effect of Partition Camping in GPU Kernels", which explains the effect of Partition Camping in more detail. It also explains the different patterns that can be used to avoid partition camping, which have been omitted in this paper for reasons of simplicity \cite{aji2011bounding}.

>>>>

		Data prefetching is relatively simple to use in the application and performs only one additional load operation, which copies memory from the global memory to the local memory. If data is loaded at this point that is no longer needed, the access times to the global memory for other threads increase unnecessarily. Additionally the execution of the current thread is only slowed down marginally, since the load operation is executed in parallel and does not block the process flow of the thread as long as the data is not required.

		The redistribution of data during the elimination of partition camping has more problems if used incorrectly. Two variants must be considered.
		In extreme cases, where all data is placed correctly, the performance gain can be reversed if the data is redistributed. 
		In a mixed case, where some data is stored unfavourably, it can lead to slight performance changes due to incorrect redistribution, but in both directions.

		Contrary to all other categories, thread block merging and thread merging have to be considered separately, since thread block merging does not normally change the number of threads, while thread merging may decrease parallelism.

@@

		If thread merging is incorrectly applied, the number of threads will be decreased. The factor depends on how many thread blocks are merged. This doubles the computing time \cite{torres2011understanding}.

@@

	Yang et. al. explains how to implement the optimizations presented in this paper. Further optimizations are also presented and these optimizations are tested using examples such as matrix multiplication with large matrices \cite{yang2010gpgpu}.

	Aji et al. explains the effect of Partition Camping in more detail. It also explains the different patterns that can be used to avoid partition camping, which have been omitted in this paper for reasons of simplicity \cite{aji2011bounding}.
